---
title: "INDE498_HW4"
author: "Steven Hwang, Haena Kim, Victoria Diaz"
date: "November 18, 2017"
output:
    html_document: 
     smart: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1 
Set an initial value for lambda = 1, beta1 = 0, and beta2 = 1. Implement the Shooting algorithm by your manual operation. Get updated values of beta1 and beta2. Do one iteration.

This has been done by hand. 

# Question 2 
Use the essential R pipeline for LASSO on this data. Compare the result from R and the result by your manual calculation. 

```{r} 
# load the data
x_1 <- c(-0.15, -0.72, 1.36, 0.61, -1.11)
x_2 <- c(-0.48, -0.54, -0.91, 1.59, 0.34) 
Y <- data.frame(Y = c(0.46, -0.37, -0.27, 1.35, -0.11))

# create the X input matrix
X <- data.frame(x_1, x_2)

# integrate all the data into a dataframe 
data <- data.frame(Y,X)
```

THIS IS UNFINISHED.

# Question 3 
(1) Write up the gaussian mixture model (GMM) that you want to estimate
(2) Estimate the parameters of your GMM model
(3) Update the labels with your estimated parameters
(4) Estimate the parameters again


# Question 4 
Use the essential R pipeline for clustering on this data. Compare the result from R and the result by your manual calculation. 

# Question 5
Consider the following data. Assume that two trees were built on it. Calculate the variable importance of each variable in RF. 
(1) Calculate the gini index of each node of both trees
(2) Estimate the importance scores of the three variables in these RF model




